Sketch Recognition and Understanding

### 2009-08-15 draft/System.tex
the commit of some svm and cite

 The vector $\omega$ determines th orientation of a seperation plane. The scalar $b$ determines the offeset of the plane from the orgin. Lets assume that the datatpointa re linearly seperable, i.e. there are infinitely many possible seperating planes that correctly classify the training data. Figure\ref{fig:svm1} illustrates two different seperating planes. It is intuitively noted from the figure that the solid line is more likely to generalize more data and thus introduce less classification error. This can be geometrically characterized as plane furthest from both classes.     % Which one is preferable ? Intuitively one perfers the solid pane since small perturbations of any point would not introduce misclassifications errors. Without any information, the solid plane is more likely to generalize better on future data. Geometrically we can characterize the solid plane as being furthuret from both classes.

@@

SVM have been applied ot the a largest MNIST a Handwritten digit recognition dataset of 60000 training set and 10000 test set\cite{IjdarSherifPaper}. Sherif and Ezzat has performed a comparision between SVM and several other techniques on the MNIST dataset. They also compared the same classfication methods on arabic handwritten digits (MADBASE) \cite{ADBase9,IjdarSherifPaper}. Their results shows that SVM classifier outperform all other techniques on both MNIST and MADBase datasets and achieved recognition rate of over 98\%. Similar results was reported by \cite{empiricalcomp11,SVMInvariantComDecoste02} on the MNIST dataset. Ther are many other successful application SVM. They have proven to be robust to noise and perform well on many tasks \cite{empiricalcomp11,Schölkopf97comparingsupport}.

>>>>

 The orientation of the speration plane is deteremined using the vector $\omega$ and the offest of the plane from the orgin is determined using the scalar $b$.  Lets assume that the datatpoint are linearly seperable, i.e. there are infinitely many possible seperating planes that correctly classify the training data. Figure\ref{fig:svm1} illustrates two different seperating planes. It is intuitively noted from the figure that the solid line is more likely to generalize more data and thus introduce less classification error. This can be geometrically characterized as plane furthest from both classes.     % Which one is preferable ? Intuitively one perfers the solid pane since small perturbations of any point would not introduce misclassifications errors. Without any information, the solid plane is more likely to generalize better on future data. Geometrically we can characterize the solid plane as being furthuret from both classes.

@@

SVM have been applied ot the a largest MNIST a Handwritten digit recognition dataset of 60000 training set and 10000 test set\cite{IjdarSherifPaper}. Sherif and Ezzat has performed a comparision between SVM and several other techniques on the MNIST dataset. They also compared the same classfication methods on arabic handwritten digits (MADBASE) \cite{ADBase9,IjdarSherifPaper}. Their results shows that SVM classifier outperform all other techniques on both MNIST and MADBase datasets and achieved recognition rate of over 98\%. Similar results was reported by \cite{empiricalcomp11,SVMInvariantComDecoste02} on the MNIST dataset. Ther are many other successful application SVM. They have proven to be robust to noise and perform well on many tasks \cite{empiricalcomp11,Scholkopf97comparingsupport}.
